### 2023-12-20 draft_jss/draft_jss.Rmd
update before 2nd round

*TF : on a pris les paramètres par défaut de reservoirpy, si j'ai bien compris, la matrice est générée par la fonction reservoirpy.mat_gen.bernoulli qui par défaut est dense (connectivity = 1)*

$W_{in}$ is a dense matrix generated using a Bernoulli (bimodal) distribution where each value can be either $-I_{scale}(m)$ or $I_{scale}(m)$ with an equal probability where  $m = 1, …, M$ corresponds to a given feature in the input layer. The input scaling, denoted $I_{scale}$, is a hyperparameter coefficient often common to all features from the input layer or specific to each feature $m$. In that case, the more important the feature is, the greater should be its input scaling. $W$ is a matrix (usually sparse) where values are generated from a Gaussian distribution $\mathcal{N}(0,1)$. Then, the $W$ matrix is scaled according to the defined spectral radius, a hyperparameter defining the highest eigen value of $W$.

>>>>

*TF : my bad, j'avais mal lu la doc. On utilise l'implémentation de base de reservoirpy qui est effectivement sparse à 0.1 par défaut.*

$W_{in}$ is a matrix (usually sparse) generated using a Bernoulli (bimodal) distribution where each value can be either $-I_{scale}(m)$ or $I_{scale}(m)$ with an equal probability where $m = 1, …, M$ corresponds to a given feature in the input layer. The input scaling, denoted $I_{scale}$, is a hyperparameter coefficient often common to all features from the input layer or specific to each feature $m$. In that case, the more important the feature is, the greater should be its input scaling. $W$ is a matrix (usually sparse) where values are generated from a Gaussian distribution $\mathcal{N}(0,1)$. Then, the $W$ matrix is scaled according to the defined spectral radius, a hyperparameter defining the highest eigen value of $W$.
